---
title: "qualtrics_pilot"
author: "Zsuzsa Szekely"
date: "2024-02-23"
output: html_document
---

```{r setup, results = 'hide'}
library(dplyr)
library(ggplot2)
library(stringr)
library(tidyr)
library(forcats)
library(ggrain)
```

```{r results = 'hide'}
# data <- read.csv('C:/Users/szeke/OneDrive - elte.hu/METASCIENCE LAB/Projects/094_PreregDeviationsQuant/Data/Study1/Source/pilot.csv')

data <- read.csv('C:/Users/szeke/OneDrive - elte.hu/METASCIENCE LAB/Projects/094_PreregDeviationsQuant/Data/Study1/Source/source_2024-03-30.csv')
```

```{r results = 'hide'}
# Drop the first two rows in the data frame and incomplete responses
data <- data %>%
  filter(consent == "Yes") %>%
  mutate(Progress = as.numeric(Progress)) %>%
  filter(Progress >= 98) %>%
  .[-c(1, 2), ]

# Drop manual responses
data <- data %>% 
  filter(Status != "Survey Preview")

# Count participants
count(data)
  
data %>% 
  count(scenario_version)
```

```{r results = 'hide'}
# Replace -99 values with NA (-99 values stand for seen but unanswered questions)
data <- data %>%
  mutate_all(~ ifelse(. == -99, NA, .))
```

#ANALYSIS

## Demographics

Descriptive analyses will be conducted about the frequency of primary research areas, the scientific career stage, the country of the institution of the participants, and whether they have conducted a preregistered study or not.

```{r results = 'hide'}
demographics <- data %>% 
  select(research_area, research_area_5_TEXT, phd_defense, phd_defense_2_TEXT, country, prereg_experience)

# Research area
## Check responses in the "Else" category
demographics %>% 
  count(research_area_5_TEXT)

## Change "Other:" to "Other"
demographics <- demographics %>%
  mutate(research_area = ifelse(research_area == "Other:", "Other", research_area))

## Plot
order_area <- c("Clinical Medicine", "Multidisciplinary", "Psychiatry / Psychology", "Social Sciences", "Other")
demographics$research_area <- factor(demographics$research_area, levels = order_area)

research_area_plot <-
  ggplot(demographics, aes(x = research_area)) +
  geom_bar(stat = "count") +
  geom_text(stat = "count", aes(label = after_stat(count)), vjust = -0.5) +
  labs(# title = "Research areas of the participants",
       x = "Research area",
       y = "Count")

ggsave("plots/research_area.png", plot = research_area_plot)

demographics %>% 
  count(research_area)

# Career stage
## Categorization: early career <10 years since PhD, mid-career = 10-20 years since PhD, late-career >20 years since PhD
demographics <- demographics %>% 
  mutate(phd_defense_2_TEXT = ifelse(!is.na(phd_defense_2_TEXT), as.numeric(phd_defense_2_TEXT), NA),
         phd_defense_2_TEXT = ifelse(phd_defense == "I haven't had a PhD defense", 2024, phd_defense_2_TEXT),
         years_since_phd = 2024 - phd_defense_2_TEXT,
         career_stage = case_when(years_since_phd < 10 ~ "early-career",
                                  years_since_phd >= 10 & years_since_phd < 20 ~ "mid-career",
                                  years_since_phd >= 20 ~ "late-career",
                                  TRUE ~ NA_character_))

order_career <- c("early-career", "mid-career", "late-career", "NA")
demographics$career_stage <- factor(demographics$career_stage, levels = order_career)

career_stages_plot <-
  ggplot(demographics, aes(x = career_stage)) +
  geom_bar(stat = "count") +
  geom_text(stat = "count", aes(label = after_stat(count)), vjust = -0.5) +
  labs(# title = "Distribution of career stages in our sample",
       x = "Career Stage",
       y = "Count")

ggsave("plots/career_stages.png", plot = career_stages_plot)

demographics %>% 
  count(career_stage)

# Country


# Preregistration experience
prereg_experience_plot <-
  ggplot(demographics, aes(x = prereg_experience)) +
  geom_bar(stat = "count") +
  geom_text(stat = "count", aes(label = after_stat(count)), vjust = -0.5) +
  labs(# title = "Experience with preregistration",
       x = "Having experience with preregistration",
       y = "Count")

ggsave("plots/prereg_experience.png", plot = prereg_experience_plot)

demographics %>% 
  count(prereg_experience)

```

## Expected consequences

Descriptive analyses (frequency of responses) of questions Q6 and Q8 will provide us with information about the expected consequences of deviations (Q6) and their reporting (Q8) on one’s professional reputation.

```{r results = 'hide'}
expected_consequences <- data %>% 
  select(prereg_experience, dev_experience, report_experience, dev_reputation_1, report_reputation_1, report_reputation_2, prereg_barriers_1, prereg_barriers_2, prereg_barriers_3, report_consequences_1, research_area)

# Experience with deviation from preregistration
expected_consequences %>% 
  filter(prereg_experience == "Yes") %>%
  # filter(dev_experience == "Yes") %>%
  count(dev_experience)

# Experience with reporting deviations
expected_consequences %>% 
  filter(prereg_experience == "Yes") %>%
  filter(dev_experience == "Yes") %>%
  filter(report_experience == "Yes") %>% 
  count()
```

```{r results = 'hide'}
# Reputation: deviation
reputation_dev <- expected_consequences %>% 
  filter(prereg_experience == "Yes") %>%
  filter(dev_experience == "Yes") # filtering data according to the display logic of the relevant survey question

order_reputation_dev <- c("I agree", "I rather agree", "I rather don't agree", "I don't agree", "I don't know")
reputation_dev$dev_reputation_1 <- factor(reputation_dev$dev_reputation_1, levels = order_reputation_dev)

reputation_dev_plot <- reputation_dev %>% 
  ggplot(aes(x = dev_reputation_1)) +
  geom_bar(stat = "count") +
  labs(# title = "Expected consequences of deviating from the preregistration",
       x = "I was concerned about my professional reputation for deviating from the preregistration.",
       y = "Count")

ggsave("plots/reputation_dev_count.png", plot = reputation_dev_plot)

## Calculate proportions
reputation_dev_plot_prop <- reputation_dev %>%
  count(dev_reputation_1) %>%
  mutate(proportion = n / sum(n) * 100)

## Plotting proportions
reputation_dev_plot_prop <- ggplot(reputation_dev_plot_prop, aes(x = dev_reputation_1, y = proportion)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = scales::percent(proportion/100)), vjust = -0.5) +
  labs(# title = "Expected consequences of deviating from the preregistration: \nPreregistering group",
       x = "I was concerned about my professional reputation for deviating from the preregistration.",
       y = "Proportion (%)") +
  coord_cartesian(ylim = c(0, 60))

ggsave("plots/reputation_dev_prop_pr.png", plot = reputation_dev_plot_prop)

# Reputation: reporting deviation
reputation_report <- expected_consequences %>%
  select(prereg_experience, dev_experience, report_experience, report_reputation_1, report_reputation_2, research_area) %>% 
  filter(prereg_experience == "Yes") %>%
  filter(dev_experience == "Yes") %>% # filtering data according to the display logic of the relevant survey question
  unite(report_reputation, report_reputation_1, report_reputation_2, sep = "", na.rm = TRUE)

order_reputation_report <- c("I agree", "I rather agree", "I rather don't agree", "I don't agree", "I don't know")
reputation_report$report_reputation <- factor(reputation_report$report_reputation, levels = order_reputation_report)

reputation_report_plot <- reputation_report %>% 
  # filter(research_area == "Social Sciences") %>% 
  ggplot(aes(x = report_reputation, 
             # fill = factor(report_experience)
             )) +
  geom_bar(stat = "count") +
  geom_text(stat = "count", aes(label = after_stat(count)), vjust = -0.5) +
  #scale_fill_manual(values = c("No" = "#db0078", "Yes" = "#9a9c60"), name = "Experience with \nreporting deviations") +
  labs(# title = "Expected consequences of not reporting deviations",
       x = "I would be concerned about my professional reputation \n for not reporting discrepancies between my \n preregistration and the final study.",
       y = "Count")

ggsave("plots/reputation_report.png", plot = reputation_report_plot)

reputation_report_plot
```

A descriptive analysis (frequency of responses) of question Q10/1 will provide us with information about the expected consequences of reporting deviations on the chances of publication.

```{r results = 'hide'}
# Chances for publication
expected_consequences_plot <-
  ggplot(expected_consequences, aes(x = report_consequences_1)) +
  geom_bar(stat = "count") +
  geom_text(stat = "count", aes(label = after_stat(count)), vjust = -0.5) +
  labs(# title = "Expected chances for publication in regards of reporting deviations",
       x = "Expected change in the chances for publication of a study due to reporting deviations",
       y = "Count") +
   scale_x_discrete(labels = c("less" = "decrease",
                               "more" = "increase",
                               "the same / equally" = "no change"))

expected_consequences_plot
  

ggsave("plots/expected_consequences.png", plot = expected_consequences_plot)
```

Descriptive analyses (frequency of responses) of question Q9 will provide us with information about what holds people back from preregistration.

```{r results = 'hide'}
# Barriers for preregistration
prereg_barriers <- expected_consequences %>%
  filter(prereg_experience == "No") %>% # filtering data according to the display logic of the relevant survey question
  pivot_longer(cols = starts_with("prereg_barriers"),
               names_to = "prereg_barrier",
               values_to = "prereg_barrier_value")

# Plot
## Define the custom order of levels
order_barriers <- c("I agree", "I rather agree", "I rather don't agree", "I don't agree", "I don't know")
prereg_barriers$prereg_barrier_value <- factor(prereg_barriers$prereg_barrier_value, levels = order_barriers)

## Define custom labels for facets
custom_labels <- c(
  prereg_barriers_1 = "Preregistration would hold me back from scientific exploration.",
  prereg_barriers_2 = "I would be concerned about my professional reputation if I deviated from my preregistration.",
  prereg_barriers_3 = "I would do preregistration if it increased the chances of my paper being published.")

## Apply labeller function to set custom labels
prereg_barriers$prereg_barrier <- factor(prereg_barriers$prereg_barrier, labels = custom_labels)

## Create the ggplot
prereg_barriers_plot <-
  ggplot(prereg_barriers, aes(x = prereg_barrier_value)) +
  geom_bar(stat = "count") +
  facet_wrap(~prereg_barrier, scales = "free_x", ncol = 1) +
  labs(# title = "Barriers for Preregistration",
       x = "Prereg Barrier Value",
       y = "Count")

ggsave("plots/prereg_barriers.png", plot = prereg_barriers_plot)

# Plot concerns for professional reputation separately
concern_plot <- prereg_barriers %>% 
  filter(prereg_barrier == "I would be concerned about my professional reputation if I deviated from my preregistration.") %>% 
  ggplot(aes(x = prereg_barrier_value)) +
  geom_bar(stat = "count") +
  labs(# title = "Expected consequences of deviating from the preregistration",
       x = "I would be concerned about my professional reputation \n for deviating from the preregistration.",
       y = "Count")

## Calculate proportions
concerns_plot_prop <- prereg_barriers %>%
  count(prereg_barrier_value) %>%
  mutate(proportion = n / sum(n) * 100)

## Plotting proportions
concerns_plot_prop <- ggplot(concerns_plot_prop, aes(x = prereg_barrier_value, y = proportion)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = scales::percent(proportion/100)), vjust = -0.5) +
  labs(# title = "Expected consequences of deviating from the preregistration: \nNon-preregistering group",
       x = "I would be concerned about my professional reputation \n for deviating from the preregistration.",
       y = "Proportion (%)") +
  coord_cartesian(ylim = c(0, 60))

ggsave("plots/reputation_dev_prop_nonpr.png", plot = concerns_plot_prop)

## Merged plot for expected consequences (prop): preregistering and non-preregistering group
concerns_pr <- reputation_dev %>%
  count(dev_reputation_1) %>%
  rename(value = dev_reputation_1) %>% 
  mutate(proportion = n / sum(n) * 100,
         is_prereg = "Preregistering")

concerns_non_pr <- prereg_barriers %>%
  count(prereg_barrier_value) %>%
  rename(value = prereg_barrier_value) %>% 
  mutate(proportion = n / sum(n) * 100,
         is_prereg = "Non-preregistering")

merged_consequences <- bind_rows(concerns_pr, concerns_non_pr)

concerns_merged_plot <- ggplot(merged_consequences, aes(x = value, y = proportion, fill = is_prereg)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = scales::percent(proportion/100)), 
            position = position_dodge(width = 1),
            vjust = -0.5) +
  labs(# title = "Expected consequences of deviating from the preregistration",
       x = "I would be concerned about my professional reputation \n for deviating from the preregistration.",
       y = "Proportion of responses within each group (%)",
       fill = "Experience with \npreregistration") +
  scale_fill_manual(values = c("Preregistering" = "#DBCF7F", "Non-preregistering" = "#db0078")) +
  coord_cartesian(ylim = c(0, 60))

concerns_merged_plot

ggsave("plots/reputation_dev_merged.png", plot = concerns_merged_plot)
```

## Scenarios

We will analyze four scenarios, assessing both the study's credibility and the researcher's trustworthiness. Our investigation aims to explore whether the fact of preregistering a study affects the assessed credibility and trustworthiness. Similarly, we will examine if the fact of deviating from the original study plan affects credibility and trustworthiness. Additionally, we will investigate potential interactions between the two aforementioned factors (preregistration and deviations) along with the assessed credibility and trustworthiness.

```{r results = 'hide'}
scenarios <- data %>% 
  select(scenario_version, assessed_cr_tr_a_1, assessed_cr_tr_a_2, assessed_cr_tr_b_1, assessed_cr_tr_b_2, assessed_cr_tr_c_1, assessed_cr_tr_c_2, assessed_cr_tr_d_1, assessed_cr_tr_d_2, cr_factors_a, cr_factors_a_9_TEXT, cr_factors_b, cr_factors_b_9_TEXT, cr_factors_c, cr_factors_c_9_TEXT, cr_factors_d, cr_factors_d_9_TEXT, tr_factors_a, tr_factors_a_9_TEXT, tr_factors_b, tr_factors_b_9_TEXT, tr_factors_c, tr_factors_c_9_TEXT, tr_factors_d, tr_factors_d_9_TEXT, fishy_c, fishy_d, report_consequences_2, report_consequences_3, research_area)

# Merge data from A, B, C, D scenarios currently stored in 4 separate variables into 1 variable per question
scenarios <- scenarios %>%
  unite(credibility, starts_with("assessed_cr_tr_") & ends_with("_1"), sep = "", na.rm = FALSE) %>%
  unite(trustworthiness, starts_with("assessed_cr_tr_") & ends_with("_2"), sep = "", na.rm = FALSE) %>% 
  unite(cr_factors, c("cr_factors_a", "cr_factors_b", "cr_factors_c", "cr_factors_d"), sep = "", na.rm = FALSE) %>%
  unite(cr_factors_text, c("cr_factors_a_9_TEXT", "cr_factors_b_9_TEXT", "cr_factors_c_9_TEXT", "cr_factors_d_9_TEXT"), sep = "", na.rm = FALSE) %>%
  unite(tr_factors, c("tr_factors_a", "tr_factors_b", "tr_factors_c", "tr_factors_d"), sep = "", na.rm = FALSE) %>%
  unite(tr_factors_text, c("tr_factors_a_9_TEXT", "tr_factors_b_9_TEXT", "tr_factors_c_9_TEXT", "tr_factors_d_9_TEXT"), sep = "", na.rm = FALSE) %>%
  unite(fishy, c("fishy_c", "fishy_d"), sep = "", na.rm = FALSE)
```

```{r results = 'hide'}
scenarios <- scenarios %>% 
  mutate(credibility = as.numeric(credibility),
         trustworthiness = as.numeric((trustworthiness))) %>% 
  group_by(scenario_version) %>% 
  mutate(N = n(),
         cr_mean = mean(credibility, na.rm = TRUE),
         cr_sd = sd(credibility, na.rm = TRUE),
         cr_se = cr_sd / sqrt(N),
         tr_mean = mean(trustworthiness, na.rm = TRUE),
         tr_sd = sd(trustworthiness, na.rm = TRUE),
         tr_se = tr_sd / sqrt(N)) %>% 
  ungroup() %>% 
  mutate(deviation = case_when(scenario_version == "A" ~ 0L,
                               scenario_version == "B" ~ 0L,
                               scenario_version == "C" ~ 1L,
                               scenario_version == "D" ~ 1L),
         prereg = case_when(scenario_version == "A" ~ 0L,
                            scenario_version == "B" ~ 1L,
                            scenario_version == "C" ~ 1L,
                            scenario_version == "D" ~ 0L))

# Credibility
credibility_plot <- scenarios %>% 
  ggplot(aes(x = deviation,
             y = cr_mean,
             group = prereg,
             color = factor(prereg))) +
  geom_path(size = 1) +
  geom_point(aes(color = factor(prereg), size = 2)) +
  geom_errorbar(aes(ymin = cr_mean - cr_se, ymax = cr_mean + cr_se), width = .1, size = 1) +
  coord_cartesian(ylim = c(50, 80)) +
  guides(size = "none") +
  #scale_shape_manual(values = c(16, 17), labels = c("Non-preregistered", "Preregistered")) +
  scale_color_manual(values = c("0" = "#db0078", "1" = "#9a9c60"),
                     labels = c("0" = "Non-Preregistered", "1" = "Preregistered")) +
  scale_x_continuous(breaks = c(0, 1), labels = c("No deviation", "Deviation")) +
  labs(shape = NULL,
       # title = "Assessed credibility of the study \nin regards of preregistration and deviations",
       x = "Deviation",
       y = "Assessed credibility (%)",
       color = NULL)

credibility_plot

# Trustworthiness
trustworthiness_plot <- scenarios %>% 
  ggplot(aes(x = deviation,
             y = tr_mean,
             group = prereg,
             color = factor(prereg))) +
  geom_path(size = 1) +
  geom_point(aes(color = factor(prereg), size = 2)) +
  geom_errorbar(aes(ymin = tr_mean - tr_se, ymax = tr_mean + tr_se), width=.1, size = 1) +
  coord_cartesian(ylim = c(50, 80)) +
  guides(size = "none") +
  # scale_shape_manual(values = c(16, 17), labels = c("Non-preregistered", "Preregistered")) +
  scale_color_manual(values = c("0" = "#db0078", "1" = "#9a9c60"),
                     labels = c("0" = "Non-Preregistered", "1" = "Preregistered")) +
  scale_x_continuous(breaks = c(0, 1), labels = c("No deviation", "Deviation")) +
  labs(shape = NULL,
       # title = "Assessed trustworthiness of the author \nin regards of preregistration and deviations",
       x = "Deviation",
       y = "Assessed trustworthiness (%)",
       color = NULL)

trustworthiness_plot

# Export plots
credibility_plot <- credibility_plot +
  theme(
    # plot.title = element_text(size = 24),  # Increase font size for plot title
    axis.title = element_text(size = 20),  # Increase font size for axis labels
    axis.text = element_text(size = 16),
    legend.text = element_text(size = 16)  # Increase font size for axis text
  )

ggsave("plots/credibility_plot.png", plot = credibility_plot, width = 10, height = 10, units = "in", dpi = 300)

trustworthiness_plot <- trustworthiness_plot +
  theme(
    # plot.title = element_text(size = 24),  # Increase font size for plot title
    axis.title = element_text(size = 20),  # Increase font size for axis labels
    axis.text = element_text(size = 16),
    legend.text = element_text(size = 16)  # Increase font size for axis text
  )

ggsave("plots/trustworthiness_plot.png", plot = trustworthiness_plot, width = 10, height = 10, units = "in", dpi = 300)
```

Plotting credibility and trustworthiness, split by research areas

```{r}
scenarios_areas <- scenarios %>%
  mutate(clinical_social = case_when(research_area == "Clinical Medicine" ~ "Clinical Medicine",
                           research_area == "Psychiatry / Psychology" ~ "Social Sciences",
                           research_area == "Social Sciences" ~ "Social Sciences",
                           TRUE ~ "Other")) %>% 
  group_by(scenario_version, clinical_social) %>% 
  mutate(N = n(),
         cr_mean = mean(credibility, na.rm = TRUE),
         cr_sd = sd(credibility, na.rm = TRUE),
         cr_se = cr_sd / sqrt(N),
         tr_mean = mean(trustworthiness, na.rm = TRUE),
         tr_sd = sd(trustworthiness, na.rm = TRUE),
         tr_se = tr_sd / sqrt(N)) %>% 
  ungroup() %>% 
  mutate(deviation = case_when(scenario_version == "A" ~ 0L,
                               scenario_version == "B" ~ 0L,
                               scenario_version == "C" ~ 1L,
                               scenario_version == "D" ~ 1L),
         prereg = case_when(scenario_version == "A" ~ 0L,
                            scenario_version == "B" ~ 1L,
                            scenario_version == "C" ~ 1L,
                            scenario_version == "D" ~ 0L))

# Credibility
## Clinical Medicine
credibility_plot_clinical <- scenarios_areas %>% 
  filter(clinical_social == "Clinical Medicine") %>% 
  ggplot(aes(x = deviation,
             y = cr_mean,
             group = prereg,
             color = factor(prereg))) +
  geom_path(size = 1) +
  geom_point(aes(color = factor(prereg), size = 2)) +
  geom_errorbar(aes(ymin = cr_mean - cr_se, ymax = cr_mean + cr_se), width = .1, size = 1) +
  coord_cartesian(ylim = c(50, 80)) +
  guides(size = "none") +
  #scale_shape_manual(values = c(16, 17), labels = c("Non-preregistered", "Preregistered")) +
  scale_color_manual(values = c("0" = "#db0078", "1" = "#9a9c60"),
                     labels = c("0" = "Non-Preregistered", "1" = "Preregistered")) +
  scale_x_continuous(breaks = c(0, 1), labels = c("No deviation", "Deviation")) +
  labs(shape = NULL,
       # title = "Assessed credibility of the study \nin regards of preregistration and deviations",
       x = "Deviation",
       y = "Assessed credibility (%)",
       color = NULL)

credibility_plot_clinical

## Social Sciences
credibility_plot_social <- scenarios_areas %>% 
  filter(clinical_social == "Social Sciences") %>% 
  ggplot(aes(x = deviation,
             y = cr_mean,
             group = prereg,
             color = factor(prereg))) +
  geom_path(size = 1) +
  geom_point(aes(color = factor(prereg), size = 2)) +
  geom_errorbar(aes(ymin = cr_mean - cr_se, ymax = cr_mean + cr_se), width = .1, size = 1) +
  coord_cartesian(ylim = c(50, 80)) +
  guides(size = "none") +
  #scale_shape_manual(values = c(16, 17), labels = c("Non-preregistered", "Preregistered")) +
  scale_color_manual(values = c("0" = "#db0078", "1" = "#9a9c60"),
                     labels = c("0" = "Non-Preregistered", "1" = "Preregistered")) +
  scale_x_continuous(breaks = c(0, 1), labels = c("No deviation", "Deviation")) +
  labs(shape = NULL,
       # title = "Assessed credibility of the study \nin regards of preregistration and deviations",
       x = "Deviation",
       y = "Assessed credibility (%)",
       color = NULL)

credibility_plot_social

## Other
credibility_plot_other <- scenarios_areas %>% 
  filter(clinical_social == "Other") %>% 
  ggplot(aes(x = deviation,
             y = cr_mean,
             group = prereg,
             color = factor(prereg))) +
  geom_path(size = 1) +
  geom_point(aes(color = factor(prereg), size = 2)) +
  geom_errorbar(aes(ymin = cr_mean - cr_se, ymax = cr_mean + cr_se), width = .1, size = 1) +
  coord_cartesian(ylim = c(50, 80)) +
  guides(size = "none") +
  #scale_shape_manual(values = c(16, 17), labels = c("Non-preregistered", "Preregistered")) +
  scale_color_manual(values = c("0" = "#db0078", "1" = "#9a9c60"),
                     labels = c("0" = "Non-Preregistered", "1" = "Preregistered")) +
  scale_x_continuous(breaks = c(0, 1), labels = c("No deviation", "Deviation")) +
  labs(shape = NULL,
       # title = "Assessed credibility of the study \nin regards of preregistration and deviations",
       x = "Deviation",
       y = "Assessed credibility (%)",
       color = NULL)

credibility_plot_other

# Trustworthiness
## Clinical Medicine
trustworthiness_plot_clinical <- scenarios_areas %>% 
  filter(clinical_social == "Clinical Medicine") %>% 
  ggplot(aes(x = deviation,
             y = tr_mean,
             group = prereg,
             color = factor(prereg))) +
  geom_path(size = 1) +
  geom_point(aes(color = factor(prereg), size = 2)) +
  geom_errorbar(aes(ymin = tr_mean - tr_se, ymax = tr_mean + tr_se), width=.1, size = 1) +
  coord_cartesian(ylim = c(50, 80)) +
  guides(size = "none") +
  # scale_shape_manual(values = c(16, 17), labels = c("Non-preregistered", "Preregistered")) +
  scale_color_manual(values = c("0" = "#db0078", "1" = "#9a9c60"),
                     labels = c("0" = "Non-Preregistered", "1" = "Preregistered")) +
  scale_x_continuous(breaks = c(0, 1), labels = c("No deviation", "Deviation")) +
  labs(shape = NULL,
       # title = "Assessed trustworthiness of the author \nin regards of preregistration and deviations",
       x = "Deviation",
       y = "Assessed trustworthiness (%)",
       color = NULL)

trustworthiness_plot_clinical

## Social Sciences
trustworthiness_plot_social <- scenarios_areas %>% 
  filter(clinical_social == "Social Sciences") %>% 
  ggplot(aes(x = deviation,
             y = tr_mean,
             group = prereg,
             color = factor(prereg))) +
  geom_path(size = 1) +
  geom_point(aes(color = factor(prereg), size = 2)) +
  geom_errorbar(aes(ymin = tr_mean - tr_se, ymax = tr_mean + tr_se), width=.1, size = 1) +
  coord_cartesian(ylim = c(50, 80)) +
  guides(size = "none") +
  # scale_shape_manual(values = c(16, 17), labels = c("Non-preregistered", "Preregistered")) +
  scale_color_manual(values = c("0" = "#db0078", "1" = "#9a9c60"),
                     labels = c("0" = "Non-Preregistered", "1" = "Preregistered")) +
  scale_x_continuous(breaks = c(0, 1), labels = c("No deviation", "Deviation")) +
  labs(shape = NULL,
       # title = "Assessed trustworthiness of the author \nin regards of preregistration and deviations",
       x = "Deviation",
       y = "Assessed trustworthiness (%)",
       color = NULL)

trustworthiness_plot_social

## Other
trustworthiness_plot_other <- scenarios_areas %>%
  filter(clinical_social == "Other") %>% 
  ggplot(aes(x = deviation,
             y = tr_mean,
             group = prereg,
             color = factor(prereg))) +
  geom_path(size = 1) +
  geom_point(aes(color = factor(prereg), size = 2)) +
  geom_errorbar(aes(ymin = tr_mean - tr_se, ymax = tr_mean + tr_se), width=.1, size = 1) +
  coord_cartesian(ylim = c(50, 80)) +
  guides(size = "none") +
  # scale_shape_manual(values = c(16, 17), labels = c("Non-preregistered", "Preregistered")) +
  scale_color_manual(values = c("0" = "#db0078", "1" = "#9a9c60"),
                     labels = c("0" = "Non-Preregistered", "1" = "Preregistered")) +
  scale_x_continuous(breaks = c(0, 1), labels = c("No deviation", "Deviation")) +
  labs(shape = NULL,
       # title = "Assessed trustworthiness of the author \nin regards of preregistration and deviations",
       x = "Deviation",
       y = "Assessed trustworthiness (%)",
       color = NULL)

trustworthiness_plot_other
```

Based on the scenario evaluations, we will have information about how people assess credibility and trustworthiness. Besides, we will also have information about the expected credibility and trustworthiness, based on Q10/2 and Q10/3 from the "Expected consequences" block of the questionnaire. By comparing these (assessed and expected) results, we will see if the assessed credibility and trustworthiness are aligned with the expected credibility and trustworthiness. To do this, we will take the expected credibility (Q10/2) results, which can take one of 3 values on a Likert scale: less, equally, or more. The participants' responses will be sorted into 3 groups according to the scale values. Within each group, we will examine how the assessed credibility results turned out: whether the participants considered the scenarios with a deviation as less, equally, or more credible than the scenarios without a deviation. This way, the expected and assessed credibility results can be compared. We will do the same analysis for the trustworthiness variable (Q10/3).

```{r results = 'hide'}
# Expected vs. assessed credibility
exp_ass_cr <- scenarios %>% 
  group_by(report_consequences_2, deviation) %>% 
  mutate(exp_ass_cr_mean = mean(credibility, na.rm = TRUE),
         exp_ass_cr_sd = sd(credibility, na.rm = TRUE)) %>% 
  ungroup()

exp_ass_cr %>% 
  count(report_consequences_2, deviation, exp_ass_cr_mean)

# Expected vs. assessed trustworthiness
exp_ass_tr <- scenarios %>% 
  group_by(report_consequences_3, deviation) %>% 
  mutate(exp_ass_tr_mean = mean(trustworthiness, na.rm = TRUE),
         exp_ass_tr_sd = sd(trustworthiness, na.rm = TRUE)) %>% 
  ungroup()

exp_ass_tr %>% 
  count(report_consequences_3, deviation, exp_ass_tr_mean)

# Plotting expected cr and tr results
exp_cr_tr <- scenarios %>% 
  select(report_consequences_2, report_consequences_3) %>% 
  rename(credibility = report_consequences_2, trustworthiness = report_consequences_3) %>% 
  pivot_longer(cols = everything(),
               names_to = "cr_tr",
               values_to = "response")

exp_cr_tr_plot <- exp_cr_tr %>% 
  ggplot(aes(x = response, fill = cr_tr)) +
  geom_bar(stat = "count", position = "dodge") +
  geom_text(stat = "count",
            aes(label = after_stat(count)),
            vjust = -0.5,
            position = position_dodge(width = 1)) +
  labs(# title = "Expected consequences of reporting deviations from the preregistration \non the perceived credibility of one's work and own trusworthiness",
       x = "Expected change in the level of the perceived credibility and trusrworthiness",
       y = "Count",
       fill = NULL) +
  scale_fill_manual(values = c("trustworthiness" = "#9a9c60", "credibility" = "#db0078"))+
  scale_x_discrete(labels = c("less" = "decrease",
                              "more" = "increase",
                              "the same / equally" = "no change"))

exp_cr_tr_plot

ggsave("plots/expected_cr_tr.png", plot = exp_cr_tr_plot)
```

We will examine whether the assessed credibility of the study and the assessed trustworthiness of the author are align with each other. Data from all four scenarios will be pooled for this analysis.

```{r results = 'hide'}
# Correlation: credibility and trustworthiness
cr_tr_plot <- scenarios %>% 
  ggplot(aes(x = credibility, y = trustworthiness)) +
  geom_point(
            #aes(color = scenario_version)
            ) +
  geom_smooth(method = "lm", se = TRUE) +
  labs(# title = "Relation Between Assessed Credibility and Trustworthiness",
       x = "Credibility",
       y = "Trustworthiness",
       # color = "Scenario version"
       )

cr_tr_plot

ggsave("plots/cr_tr.png", plot = cr_tr_plot)

# Calculate correlation
correlation <- cor(scenarios$credibility, scenarios$trustworthiness)
correlation
```

Descriptive analyses (frequency of responses) of questions Q14 and Q15 will show what factors are mostly considered when assessing credibility and trustworthiness.

```{r results = 'hide'}
# Credibility factors
factors_cr <- scenarios %>% 
  separate_rows(cr_factors, sep = ",") %>%
  mutate(cr_factors = fct_relevel(cr_factors, "other:", after = Inf)) %>% 
  mutate(cr_factors = fct_rev(cr_factors)) %>% 
  mutate(cr_factors = fct_relabel(cr_factors, ~gsub(":", "", .)))

factors_cr_plot <- factors_cr %>%
  ggplot(aes(y = cr_factors)) +
  geom_bar() +
  labs(# title = "Factors Considered When Assessing the \nCredibility of a Study",
       x = "Count",
       y = "Factors") +
  coord_cartesian(xlim = c(0, 1000))

# Trustworthiness factors
factors_tr <- scenarios %>% 
  separate_rows(tr_factors, sep = ",") %>%
  mutate(tr_factors = fct_relevel(tr_factors, "other:", after = Inf)) %>% 
  mutate(tr_factors = fct_rev(tr_factors)) %>% 
  mutate(tr_factors = fct_relabel(tr_factors, ~gsub(":", "", .)))

factors_tr_plot <- factors_tr %>%
  ggplot(aes(y = tr_factors)) +
  geom_bar() +
  labs(# title = "Factors Considered When Assessing the \nTrustworthiness of an Author",
       x = "Count",
       y = "Factors") +
  coord_cartesian(xlim = c(0, 1000))

# Export
ggsave("plots/factors_cr.png", plot = factors_cr_plot, units = "in", dpi = 300)
ggsave("plots/factors_tr.png", plot = factors_tr_plot, units = "in", dpi = 300)

```

```{r}
# Fishy
fishy <- scenarios %>% 
  filter(scenario_version == c("C", "D"))

fishy_plot <- fishy %>% 
  ggplot(aes(x = fishy)) +
  geom_text(stat = "count", aes(label = after_stat(count)), vjust = -0.5) +
  geom_bar() +
  geom_bar() +
  labs(# title = "Evaluation of the deviation from the original plan",
       x = "Evaluation of the deviation",
       y = "Count")

fishy_plot

# Export
ggsave("plots/fishy.png", plot = fishy_plot, units = "in", dpi = 300)
```

## Perception of practices

Descriptive analyses will be conducted to examine the distribution of responses to all 3 questions of Q17. These analyses will inform us about how researchers perceive others' practices regarding deviating from preregistration (Q17/1), reporting discrepancies (Q147/2), and comparing preregistrations to the corresponding papers (Q17/3).

```{r results = 'hide'}
practices_perception <- data %>% 
  select(practices_perception_1, practices_perception_2, practices_perception_3)

# Plot
## Transform data for plotting
practices_perception <- practices_perception %>%
  rename(
    deviation = practices_perception_1,
    reporting = practices_perception_2,
    checking = practices_perception_3) %>% 
  pivot_longer(cols = everything(),
               names_to = "practice",
               values_to = "perceived_frequency") %>% 
  mutate(perceived_frequency = as.numeric(perceived_frequency))

## Create the ggplot
practices_perception_plot <-
  ggplot(practices_perception, aes(x = perceived_frequency)) +
  geom_histogram(binwidth = 10) +
  facet_wrap(~practice, ncol = 1) +
  labs(# title = "Perception of Others' Practices",
       x = "Frequency of Adopting the Practice (%)",
       y = "Count")

ggsave("plots/practices_perception.png", plot = practices_perception_plot)
```

## Incentives and support

Descriptive analyses will examine the frequency of responses to Q18, Q19, Q20, and Q21.

```{r results = 'hide'}
incentives <- data %>% 
  select(requirement, requirement_5_TEXT, guidance, guidance_5_TEXT, norms, training)

# Requirement
requirements <- incentives %>%
  separate_rows(requirement, sep = ",") %>%
  mutate(requirement = fct_relevel(requirement, "none", "else:", after = Inf)) %>% 
  mutate(requirement = fct_rev(requirement)) %>% 
  mutate(requirement = fct_relabel(requirement, ~gsub(":", "", .)))

requirements_plot <-
  requirements %>% 
  ggplot(aes(y = requirement)) +
  geom_bar() +
  labs(# title = "Requirement of Reporting Discrepancies",
       x = "Count",
       y = "Stakeholders setting the requirement") +
  scale_y_discrete(labels = c("my PI or collaborators." = "PI / collaboratos",
                              "the funder of my research project." = "funder",
                              "the journal where I would like to submit my paper/I have submitted my paper." = "journal"))

# Guidance
guidance <- incentives %>%
  separate_rows(guidance, sep = ",") %>%
  mutate(guidance = fct_relevel(guidance, "none", "else:", after = Inf)) %>% 
  mutate(guidance = fct_rev(guidance)) %>% 
  mutate(guidance = fct_relabel(guidance, ~gsub(":", "", .)))

guidance_plot <-
  guidance %>% 
  ggplot(aes(y = guidance)) +
  geom_bar() +
  labs(# title = "Guidance on Reporting Discrepancies",
       x = "Count",
       y = "Stakeholders providing guidance") +
  scale_y_discrete(labels = c("my PI or collaborators." = "PI / collaboratos",
                              "the funder of my research project." = "funder",
                              "the journal where I would like to submit my paper/I have submitted my paper." = "journal"))

# Norms
norms <- incentives %>% 
  mutate(norms = factor(norms, levels = c("I agree", "I rather agree", "I rather don't agree", "I don't agree", "I don't know"))) %>% 
   mutate(norms = fct_rev(norms))

norms_plot <-
  norms %>% 
  ggplot(aes(y = norms)) +
  geom_bar() +
  labs(# title = "Institutional Norms Serving as Motivation for Reporting Discrepancies",
       x = "Count",
       y = "Level of agreement")


# Training
trainings <- incentives %>%
  mutate(training = factor(training, levels = c("Yes", "No", "I don't know"))) %>% 
  mutate(training = fct_rev(training))

trainings_plot <-
  trainings %>% 
  ggplot(aes(y = training)) +
  geom_bar() +
  labs(# title = "Availability of Trainings on Preregistration",
       x = "Count",
       y = "Availability") +
  scale_y_discrete(labels = c("I don't know" = "Don't know"))

# Export
ggsave("plots/requirements.png", plot = requirements_plot)
ggsave("plots/guidance.png", plot = guidance_plot)
ggsave("plots/norms.png", plot = norms_plot)
ggsave("plots/trainings.png", plot = trainings_plot)
```


```{r results = 'hide'}

```
