---
title: "qualtrics_pilot"
author: "Zsuzsa Szekely"
date: "2024-02-23"
output: html_document
---

```{r setup, results = 'hide'}
library(dplyr)
library(ggplot2)
library(stringr)
library(tidyr)
library(forcats)
```

```{r results = 'hide'}
# data <- read.csv('C:/Users/szeke/OneDrive - elte.hu/METASCIENCE LAB/Projects/094_PreregDeviationsQuant/Data/Study1/Source/pilot.csv')

data <- read.csv('C:/Users/szeke/OneDrive - elte.hu/METASCIENCE LAB/Projects/094_PreregDeviationsQuant/Data/Study1/Source/generated_pilot.csv')
```

```{r results = 'hide'}
# Drop the first two rows in the data frame and incomplete responses
data <- data[-c(1, 2), ] %>% 
  filter(consent == "Yes") %>% 
  filter(Progress == 100)

# Drop manual responses
data <- data %>% 
  filter(Status != "Survey Preview")

# Count participants
count(data)
  
data %>% 
  count(scenario_version)
```

```{r results = 'hide'}
# Replace -99 values with NA (-99 values stand for seen but unanswered questions)
data <- data %>%
  mutate_all(~ ifelse(. == -99, NA, .))
```

#ANALYSIS

## Demographics

Descriptive analyses will be conducted about the frequency of primary research areas, the scientific career stage, the country of the institution of the participants, and whether they have conducted a preregistered study or not.

```{r results = 'hide'}
demographics <- data %>% 
  select(research_area, research_area_5_TEXT, phd_defense, phd_defense_2_TEXT, country, prereg_experience)

# Research area
## Check responses in the "Else" category
demographics %>% 
  count(research_area_5_TEXT)

## If someone chose "Else", put "Else" into the research_area variable
demographics <- demographics %>% 
  mutate(research_area = ifelse(!is.na(research_area_5_TEXT) & research_area_5_TEXT != "", "Else", research_area))

## Plot
ggplot(demographics, aes(x = research_area)) +
  geom_bar(stat = "count") +
  labs(title = "Research Areas of Participants",
       x = "Research Area",
       y = "Count")

# Career stage
## Categorization: early career <10 years since PhD, mid-career = 11-20 years since PhD, late-career >20 years since PhD
demographics <- demographics %>% 
  mutate(phd_defense_2_TEXT = ifelse(!is.na(phd_defense_2_TEXT), as.numeric(phd_defense_2_TEXT), NA),
         phd_defense_2_TEXT = ifelse(phd_defense == "I haven't had a PhD defense", 2024, phd_defense_2_TEXT),
         years_since_phd = 2024 - phd_defense_2_TEXT,
         career_stage = case_when(years_since_phd < 10 ~ "early-career",
                                  years_since_phd >= 10 & years_since_phd < 20 ~ "mid-career",
                                  years_since_phd >= 20 ~ "late-career",
                                  TRUE ~ NA_character_))

ggplot(demographics, aes(x = career_stage)) +
  geom_bar(stat = "count") +
  labs(title = "Distribution of Career Stages",
       x = "Career Stage",
       y = "Count")

# Country


# Preregistration experience
ggplot(demographics, aes(x = prereg_experience)) +
  geom_bar(stat = "count") +
  labs(title = "Experience With Preregistration",
       x = "Having Experience with Preregistration",
       y = "Count")

```

## Expected consequences

Descriptive analyses (frequency of responses) of questions Q6 and Q8 will provide us with information about the expected consequences of deviations (Q6) and their reporting (Q8) on one’s professional reputation.

```{r results = 'hide'}
expected_consequences <- data %>% 
  select(prereg_experience, dev_experience, report_experience, dev_reputation_1, report_reputation_1, report_reputation_2, prereg_barriers_1, prereg_barriers_2, prereg_barriers_3, report_consequences_1)

# Experience with deviation from preregistration
expected_consequences %>% 
  filter(prereg_experience == "Yes") %>%
  # filter(dev_experience == "Yes") %>%
  count(dev_experience)

# Experience with reporting deviations
expected_consequences %>% 
  filter(prereg_experience == "Yes") %>%
  filter(dev_experience == "Yes") %>%
  filter(report_experience == "Yes") %>% 
  count()
```

```{r results = 'hide'}
# Reputation: deviation
reputation_dev <- expected_consequences %>% 
  filter(prereg_experience == "Yes") %>%
  filter(dev_experience == "Yes") # filtering data according to the display logic of the relevant survey question

ggplot(reputation_dev, aes(x = dev_reputation_1)) +
  geom_bar(stat = "count") +
  labs(title = "Expected Consequences of Deviating from the Preregistration",
       x = "I was concerned about my professional reputation for deviating from the preregistration.",
       y = "Count")
  

# Reputation: reporting deviation
reputation_report <- expected_consequences %>%
  select(prereg_experience, dev_experience, report_experience, report_reputation_1, report_reputation_2) %>% 
  filter(prereg_experience == "Yes") %>%
  filter(dev_experience == "Yes") %>% # filtering data according to the display logic of the relevant survey question
  unite(report_reputation, report_reputation_1, report_reputation_2, sep = "", na.rm = TRUE)
 

ggplot(reputation_report, aes(x = report_reputation, fill = factor(report_experience))) +
  geom_bar(stat = "count") +
  scale_fill_manual(values = c("No" = "pink", "Yes" = "skyblue"), name = "Experience with \nreporting deviations") +
  labs(title = "Expected Consequences of Not Reporting Deviations",
       x = "I would be concerned about my professional reputation \n for not reporting discrepancies between my \n preregistration and the final study.",
       y = "Count")
```

A descriptive analysis (frequency of responses) of question Q10/1 will provide us with information about the expected consequences of reporting deviations on the chances of publication.

```{r results = 'hide'}
# Chances for publication
ggplot(expected_consequences, aes(x = report_consequences_1)) +
  geom_bar(stat = "count") +
  labs(title = "Expected Chances for Publication in Light of Reporting Deviations",
       x = "If I reported the deviations between the preregistration and the study, \n my paper would have ... chance to be published as if I did not report them.",
       y = "Count") +
   scale_x_discrete(labels = c("the same / equally" = "same"))
```

Descriptive analyses (frequency of responses) of question Q9 will provide us with information about what holds people back from preregistration.

```{r results = 'hide'}
# Barriers for preregistration
prereg_barriers <- expected_consequences %>%
  filter(prereg_experience == "No") %>% # filtering data according to the display logic of the relevant survey question
  pivot_longer(cols = starts_with("prereg_barriers"),
               names_to = "prereg_barrier",
               values_to = "prereg_barrier_value")

# Plot
## Define the custom order of levels
custom_order <- c("I agree", "I rather agree", "I rather don't agree", "I don't agree", "I don't know")

## Define custom labels for facets
custom_labels <- c(
  prereg_barriers_1 = "Preregistration would hold me back from scientific exploration.",
  prereg_barriers_2 = "I would be concerned about my professional reputation if I deviated from my preregistration.",
  prereg_barriers_3 = "I would do preregistration if it increased the chances of my paper being published.")

## Apply labeller function to set custom labels
prereg_barriers$prereg_barrier <- factor(prereg_barriers$prereg_barrier, labels = custom_labels)

## Create the ggplot
ggplot(prereg_barriers, aes(x = prereg_barrier_value)) +
  geom_bar(stat = "count") +
  facet_wrap(~prereg_barrier, scales = "free_x", ncol = 1) +
  labs(title = "Barriers for Preregistration",
       x = "Prereg Barrier Value",
       y = "Count")
```

## Scenarios

We will analyze four scenarios, assessing both the study's credibility and the researcher's trustworthiness. Our investigation aims to explore whether the fact of preregistering a study affects the assessed credibility and trustworthiness. Similarly, we will examine if the fact of deviating from the original study plan affects credibility and trustworthiness. Additionally, we will investigate potential interactions between the two aforementioned factors (preregistration and deviations) along with the assessed credibility and trustworthiness.

```{r results = 'hide'}
scenarios <- data %>% 
  select(scenario_version, assessed_cr_tr_a_1, assessed_cr_tr_a_2, assessed_cr_tr_b_1, assessed_cr_tr_b_2, assessed_cr_tr_c_1, assessed_cr_tr_c_2, assessed_cr_tr_d_1, assessed_cr_tr_d_2, cr_factors_a, cr_factors_a_9_TEXT, cr_factors_b, cr_factors_b_9_TEXT, cr_factors_c, cr_factors_c_9_TEXT, cr_factors_d, cr_factors_d_9_TEXT, tr_factors_a, tr_factors_a_9_TEXT, tr_factors_b, tr_factors_b_9_TEXT, tr_factors_c, tr_factors_c_9_TEXT, tr_factors_d, tr_factors_d_9_TEXT, fishy_c, fishy_d, report_consequences_2, report_consequences_3)

# Merge data from A, B, C, D scenarios currently stored in 4 separate variables into 1 variable per question
scenarios <- scenarios %>%
  unite(credibility, starts_with("assessed_cr_tr_") & ends_with("_1"), sep = "", na.rm = FALSE) %>%
  unite(trustworthiness, starts_with("assessed_cr_tr_") & ends_with("_2"), sep = "", na.rm = FALSE) %>% 
  unite(cr_factors, c("cr_factors_a", "cr_factors_b", "cr_factors_c", "cr_factors_d"), sep = "", na.rm = FALSE) %>%
  unite(cr_factors_text, c("cr_factors_a_9_TEXT", "cr_factors_b_9_TEXT", "cr_factors_c_9_TEXT", "cr_factors_d_9_TEXT"), sep = "", na.rm = FALSE) %>%
  unite(tr_factors, c("tr_factors_a", "tr_factors_b", "tr_factors_c", "tr_factors_d"), sep = "", na.rm = FALSE) %>%
  unite(tr_factors_text, c("tr_factors_a_9_TEXT", "tr_factors_b_9_TEXT", "tr_factors_c_9_TEXT", "tr_factors_d_9_TEXT"), sep = "", na.rm = FALSE) %>%
  unite(fishy, c("fishy_c", "fishy_d"), sep = "", na.rm = FALSE)
```

```{r results = 'hide'}
scenarios <- scenarios %>% 
  mutate(credibility = as.numeric(credibility),
         trustworthiness = as.numeric((trustworthiness))) %>% 
  group_by(scenario_version) %>% 
  mutate(N = n(),
         cr_mean = mean(credibility, na.rm = TRUE),
         cr_sd = sd(credibility, na.rm = TRUE),
         cr_se = cr_sd / sqrt(N),
         tr_mean = mean(trustworthiness, na.rm = TRUE),
         tr_sd = sd(trustworthiness, na.rm = TRUE),
         tr_se = tr_sd / sqrt(N)) %>% 
  ungroup() %>% 
  mutate(deviation = case_when(scenario_version == "A" ~ 0L,
                               scenario_version == "B" ~ 0L,
                               scenario_version == "C" ~ 1L,
                               scenario_version == "D" ~ 1L),
         prereg = case_when(scenario_version == "A" ~ 0L,
                            scenario_version == "B" ~ 1L,
                            scenario_version == "C" ~ 1L,
                            scenario_version == "D" ~ 0L))

# Credibility
credibility_plot <- scenarios %>% 
  ggplot(aes(x = deviation,
             y = cr_mean,
             group = prereg)) +
  geom_path() +
  geom_point(aes(shape = factor(prereg), size = 2)) +
  geom_errorbar(aes(ymin = cr_mean - cr_se, ymax = cr_mean + cr_se), width=.1) +
  guides(size = "none") +
  scale_shape_manual(values = c(16, 17), labels = c("Non-preregistered", "Preregistered")) +
  scale_x_continuous(breaks = c(0, 1), labels = c("No deviation", "Deviation")) +
  labs(shape = NULL,
       title = "Credibility in Light of Preregistration",
       x = "Deviation",
       y = "Credibility")

credibility_plot

# Trustworthiness
trustworthiness_plot <- scenarios %>% 
  ggplot(aes(x = deviation,
             y = tr_mean,
             group = prereg)) +
  geom_path() +
  geom_point(aes(shape = factor(prereg), size = 2)) +
  geom_errorbar(aes(ymin = tr_mean - tr_se, ymax = tr_mean + tr_se), width=.1) +
  guides(size = "none") +
  scale_shape_manual(values = c(16, 17), labels = c("Non-preregistered", "Preregistered")) +
  scale_x_continuous(breaks = c(0, 1), labels = c("No deviation", "Deviation")) +
  labs(shape = NULL,
       title = "Trustworthiness in Light of Preregistration",
       x = "Deviation",
       y = "Credibility")

trustworthiness_plot
```

Based on the scenario evaluations, we will have information about how people assess credibility and trustworthiness. Besides, we will also have information about the expected credibility and trustworthiness, based on Q10/2 and Q10/3 from the "Expected consequences" block of the questionnaire. By comparing these (assessed and expected) results, we will see if the assessed credibility and trustworthiness are aligned with the expected credibility and trustworthiness. To do this, we will take the expected credibility (Q10/2) results, which can take one of 3 values on a Likert scale: less, equally, or more. The participants' responses will be sorted into 3 groups according to the scale values. Within each group, we will examine how the assessed credibility results turned out: whether the participants considered the scenarios with a deviation as less, equally, or more credible than the scenarios without a deviation. This way, the expected and assessed credibility results can be compared. We will do the same analysis for the trustworthiness variable (Q10/3).

```{r results = 'hide'}
# Expected vs. assessed credibility
exp_ass_cr <- scenarios %>% 
  group_by(report_consequences_2, deviation) %>% 
  mutate(exp_ass_cr_mean = mean(credibility, na.rm = TRUE),
         exp_ass_cr_sd = sd(credibility, na.rm = TRUE)) %>% 
  ungroup()

exp_ass_cr %>% 
  count(report_consequences_2, deviation, exp_ass_cr_mean)

# Expected vs. assessed trustworthiness
exp_ass_tr <- scenarios %>% 
  group_by(report_consequences_3, deviation) %>% 
  mutate(exp_ass_tr_mean = mean(trustworthiness, na.rm = TRUE),
         exp_ass_tr_sd = sd(trustworthiness, na.rm = TRUE)) %>% 
  ungroup()

exp_ass_tr %>% 
  count(report_consequences_3, deviation, exp_ass_tr_mean)
```

We will examine whether the assessed credibility of the study and the assessed trustworthiness of the author are align with each other. Data from all four scenarios will be pooled for this analysis.

```{r results = 'hide'}
# Correlation: credibility and trustworthiness
cr_tr_plot <- scenarios %>% 
  ggplot(aes(x = credibility, y = trustworthiness)) +
  geom_point(aes(color = scenario_version)) +
  geom_smooth(method = "lm", se = TRUE) +
  labs(title = "Relation Between Assessed Credibility and Trustworthiness",
       x = "Credibility",
       y = "Trustworthiness",
       color = "Scenario version")

cr_tr_plot
```

Descriptive analyses (frequency of responses) of questions Q14 and Q15 will show what factors are mostly considered when assessing credibility and trustworthiness.

```{r results = 'hide'}
# Credibility factors
factors_cr <- scenarios %>% 
  separate_rows(cr_factors, sep = ",") %>%
  mutate(cr_factors = fct_relevel(cr_factors, "other:", after = Inf)) %>% 
  mutate(cr_factors = fct_rev(cr_factors)) %>% 
  mutate(cr_factors = fct_relabel(cr_factors, ~gsub(":", "", .)))

factors_cr %>%
  ggplot(aes(y = cr_factors)) +
  geom_bar() +
  labs(title = "Factors Considered When Assessing the \nCredibility of a Study",
       x = "Count",
       y = "Factors")

# Trustworthiness factors
factors_tr <- scenarios %>% 
  separate_rows(tr_factors, sep = ",") %>%
  mutate(tr_factors = fct_relevel(tr_factors, "other:", after = Inf)) %>% 
  mutate(tr_factors = fct_rev(tr_factors)) %>% 
  mutate(tr_factors = fct_relabel(tr_factors, ~gsub(":", "", .)))

factors_tr %>%
  ggplot(aes(y = tr_factors)) +
  geom_bar() +
  labs(title = "Factors Considered When Assessing the \nTrustworthiness of an Author",
       x = "Count",
       y = "Factors")

```

## Perception of practices

Descriptive analyses will be conducted to examine the distribution of responses to all 3 questions of Q17. These analyses will inform us about how researchers perceive others' practices regarding deviating from preregistration (Q17/1), reporting discrepancies (Q147/2), and comparing preregistrations to the corresponding papers (Q17/3).

```{r results = 'hide'}
practices_perception <- data %>% 
  select(practices_perception_1, practices_perception_2, practices_perception_3)

# Plot
## Transform data for plotting
practices_perception <- practices_perception %>%
  rename(
    deviation = practices_perception_1,
    reporting = practices_perception_2,
    checking = practices_perception_3) %>% 
  pivot_longer(cols = everything(),
               names_to = "practice",
               values_to = "perceived_frequency") %>% 
  mutate(perceived_frequency = as.numeric(perceived_frequency))

## Create the ggplot
ggplot(practices_perception, aes(x = perceived_frequency)) +
  geom_histogram(binwidth = 10) +
  facet_wrap(~practice, ncol = 1) +
  labs(title = "Perception of Others' Practices",
       x = "Frequency of Conducting the Practice (%)",
       y = "Count")
```

## Incentives and support

Descriptive analyses will examine the frequency of responses to Q18, Q19, Q20, and Q21.

```{r results = 'hide'}
incentives <- data %>% 
  select(requirement, requirement_5_TEXT, guidance, guidance_5_TEXT, norms, training)

# Requirement
requirements <- incentives %>%
  separate_rows(requirement, sep = ",") %>%
  mutate(requirement = fct_relevel(requirement, "none", "else:", after = Inf)) %>% 
  mutate(requirement = fct_rev(requirement)) %>% 
  mutate(requirement = fct_relabel(requirement, ~gsub(":", "", .)))

requirements %>% 
  ggplot(aes(y = requirement)) +
  geom_bar() +
  labs(title = "Requirement of Reporting Discrepancies",
       x = "Count",
       y = "Stakeholders setting the requirement") +
  scale_y_discrete(labels = c("my PI or collaborators." = "PI / collaboratos",
                              "the funder of my research project." = "funder",
                              "the journal where I would like to submit my paper/I have submitted my paper." = "journal"))

# Guidance
guidance <- incentives %>%
  separate_rows(guidance, sep = ",") %>%
  mutate(guidance = fct_relevel(guidance, "none", "else:", after = Inf)) %>% 
  mutate(guidance = fct_rev(guidance)) %>% 
  mutate(guidance = fct_relabel(guidance, ~gsub(":", "", .)))

guidance %>% 
  ggplot(aes(y = guidance)) +
  geom_bar() +
  labs(title = "Guidance on Reporting Discrepancies",
       x = "Count",
       y = "Stakeholders providing guidance") +
  scale_y_discrete(labels = c("my PI or collaborators." = "PI / collaboratos",
                              "the funder of my research project." = "funder",
                              "the journal where I would like to submit my paper/I have submitted my paper." = "journal"))

# Norms
norms <- incentives %>% 
  mutate(norms = factor(norms, levels = c("I agree", "I rather agree", "I rather don't agree", "I don't agree", "I don't know"))) %>% 
   mutate(norms = fct_rev(norms))

norms %>% 
  ggplot(aes(y = norms)) +
  geom_bar() +
  labs(title = "Institutional Norms Serving as Motivation for Reporting Discrepancies",
       x = "Count",
       y = "Level of agreement")


# Training
trainings <- incentives %>%
  mutate(training = factor(training, levels = c("Yes", "No", "I don't know"))) %>% 
  mutate(training = fct_rev(training))

trainings %>% 
  ggplot(aes(y = training)) +
  geom_bar() +
  labs(title = "Availability of Trainings on Reporting Discrepancies",
       x = "Count",
       y = "Availability")+
  scale_y_discrete(labels = c("I don't know" = "Don't know"))
```


```{r results = 'hide'}

```
